¥section{Backpropagation}

¥subsection{Backward Pipeline}

¥FormulaName{Dense-layer reverse flow}
¥[
dA^{[l]} ¥to dZ^{[l]} ¥to dW^{[l]}, db^{[l]} ¥to dA^{[l-1]}.
¥]
¥Use{Reverse-mode differentiation for dense layers.}

¥subsection{Output Layer Simplifications}

¥FormulaName{Sigmoid output with binary cross-entropy}
¥[
dZ^{[L]} = A^{[L]} - Y.
¥]
¥Shapes{$A^{[L]}, Y, dZ^{[L]} ¥in ¥R^{1 ¥times m}$.}
¥Use{Binary output-layer gradient.}

¥FormulaName{Softmax output with categorical cross-entropy}
¥[
dZ^{[L]} = A^{[L]} - Y.
¥]
¥Shapes{$A^{[L]}, Y, dZ^{[L]} ¥in ¥R^{K ¥times m}$.}
¥Use{Multi-class output-layer gradient.}
¥Notes{Same compact form, different output dimension.}

¥subsection{General Hidden-Layer Backpropagation}

¥FormulaName{Activation gradient}
¥[
dZ^{[l]}
=
dA^{[l]} ¥hadamard g'^{[l]}(Z^{[l]}).
¥]
¥Shapes{$dA^{[l]}, dZ^{[l]}, Z^{[l]} ¥in ¥R^{n^{[l]} ¥times m}$.}
¥Use{Hidden-layer pre-activation gradient.}

¥FormulaName{Previous-activation gradient}
¥[
dA^{[l-1]}
=
(W^{[l]})¥transpose dZ^{[l]}.
¥]
¥[
W^{[l]} ¥in ¥R^{n^{[l]} ¥times n^{[l-1]}},
¥qquad
dA^{[l-1]} ¥in ¥R^{n^{[l-1]} ¥times m}.
¥]
¥Use{Gradient passed to previous layer.}

¥FormulaName{Shape check for $dA^{[l-1]}$}
¥[
(W^{[l]})¥transpose dZ^{[l]}
:
(n^{[l-1]} ¥times n^{[l]})
¥cdot
(n^{[l]} ¥times m)
¥to
n^{[l-1]} ¥times m.
¥]
¥Use{Backpropagation dimension check.}

¥subsection{Parameter Gradients}

¥FormulaName{Weight gradient}
¥[
dW^{[l]}
=
¥frac{1}{m}
dZ^{[l]}(A^{[l-1]})¥transpose.
¥]
¥Shapes{$dW^{[l]} ¥in ¥R^{n^{[l]} ¥times n^{[l-1]}}$.}
¥Use{Dense-layer weight gradient.}

¥FormulaName{Bias gradient}
¥[
db^{[l]}
=
¥frac{1}{m}
¥sum_{i=1}^{m}
dZ^{[l](i)}
¥in
¥R^{n^{[l]} ¥times 1}.
¥]
¥Use{Dense-layer bias gradient.}
¥Notes{$dZ^{[l](i)}$ is the $i$-th column of $dZ^{[l]}$.}

¥FormulaName{Shape check for $dW^{[l]}$}
¥[
dZ^{[l]}(A^{[l-1]})¥transpose
:
(n^{[l]} ¥times m)
¥cdot
(m ¥times n^{[l-1]})
¥to
n^{[l]} ¥times n^{[l-1]}.
¥]
¥Use{Parameter-gradient dimension check.}

¥subsection{Shape Check and Parameter Update Link}

¥FormulaName{Basic gradient descent update}
¥[
¥begin{aligned}
W^{[l]} &¥leftarrow W^{[l]} - ¥alpha dW^{[l]},¥¥
b^{[l]} &¥leftarrow b^{[l]} - ¥alpha db^{[l]}.
¥end{aligned}
¥]
¥Shapes{$W^{[l]},dW^{[l]} ¥in ¥R^{n^{[l]} ¥times n^{[l-1]}}$; $b^{[l]},db^{[l]} ¥in ¥R^{n^{[l]} ¥times 1}$.}
¥Use{Basic gradient descent update.}

¥subsection{Symbols and Shapes}

¥begin{center}
¥begin{tabular}{lll}
¥toprule
Symbol & Meaning & Shape ¥¥
¥midrule
$A^{[l-1]}$ & previous activation & $¥R^{n^{[l-1]} ¥times m}$ ¥¥
$Z^{[l]}$ & pre-activation & $¥R^{n^{[l]} ¥times m}$ ¥¥
$A^{[l]}$ & activation & $¥R^{n^{[l]} ¥times m}$ ¥¥
$W^{[l]}$ & layer weights & $¥R^{n^{[l]} ¥times n^{[l-1]}}$ ¥¥
$b^{[l]}$ & layer bias & $¥R^{n^{[l]} ¥times 1}$ ¥¥
$dA^{[l]}$ & activation gradient & $¥R^{n^{[l]} ¥times m}$ ¥¥
$dZ^{[l]}$ & pre-activation gradient & $¥R^{n^{[l]} ¥times m}$ ¥¥
$dW^{[l]}$ & weight gradient & $¥R^{n^{[l]} ¥times n^{[l-1]}}$ ¥¥
$db^{[l]}$ & bias gradient & $¥R^{n^{[l]} ¥times 1}$ ¥¥
$g'^{[l]}$ & activation derivative & elementwise map ¥¥
$m$ & batch size & $¥mathbb{N}$ ¥¥
$n^{[l]}$ & units in layer $l$ & $¥mathbb{N}$ ¥¥
¥bottomrule
¥end{tabular}
¥end{center}
